The SMT Competition 2015--2018

### 2019-03-19 2018/report/SMT-COMP.tex
Remove Figure 2 (Distribution of SMT-LIB benchmarks by file size)
Avoid unfortunate line break

The 2018 release of the SMT Library contained 336,844 non-incremental
benchmarks in 51 logics, as well as~10,167 incremental benchmarks
(with a total of nearly 32 million {\tt check-sat} commands) in 26
logics.  Table~\ref{table:smtlib} presents further data on the size of
the SMT Library since~2015.  While the library usually grows from one
year to the next because of the inclusion of new benchmarks and
logics, continuous curation efforts may also cause benchmarks to be
removed or reclassified on occasion, thereby causing individual logics
or even the entire library to shrink.  From~2015 to~2018, the total
number of benchmarks has increased by~68\,\%.
Figure~\ref{fig:benchmark-sizes} shows how the file size of individual
benchmarks is distributed.  The largest benchmark in the 2018 release
had a size of 1,041~MB; the total size of the release was 91~GB.

@@

\begin{figure}
  \centering
  \scalebox{.96}[.96]{\begin{tikzpicture}
    \draw [gray] (0,0) -- (14,0);
    \draw [gray] (0,.9) -- (14,.9);
    \draw [gray] (0,1.8) -- (14,1.8);
    \draw [gray] (0,2.7) -- (14,2.7);
    \draw [gray] (0,3.6) -- (14,3.6);
    \draw [gray] (0,4.5) -- (14,4.5);
    \draw [gray] (0,5.4) -- (14,5.4);

    \node [left] at (0,0) {\footnotesize 0};
    \node [left] at (0,.9) {\footnotesize 1};
    \node [left] at (0,1.8) {\footnotesize 10};
    \node [left] at (0,2.7) {\footnotesize 100};
    \node [left] at (0,3.6) {\footnotesize 1000};
    \node [left] at (0,4.5) {\footnotesize 10000};
    \node [left] at (0,5.4) {\footnotesize 100000};

    \node [rotate=90] at (-1.5,2.7) {\small Benchmarks};

    \draw [fill=black] (0.5,0) rectangle (1,5.1629791157); % 54531
    \draw [fill=black] (2.25,0) rectangle (2.75,5.5836542368); % 159978
    \draw [fill=black] (4,0) rectangle (4.5,5.350394013); % 88081
    \draw [fill=black] (5.75,0) rectangle (6.25,4.8786283826); % 26345
    \draw [fill=black] (7.5,0) rectangle (8,4.3889077926); % 7526
    \draw [fill=black] (9.25,0) rectangle (9.75,3.1918883971); % 352
    \draw [fill=black] (11,0) rectangle (11.5,2.2422255245); % 31
    %\draw [fill=black] (12.75,0) rectangle (13.25,0); % 0

    \draw [fill=white] (1,0) rectangle (1.5,1.4418539922); % 4
    \draw [fill=white] (2.75,0) rectangle (3.25,3.8742353084); % 2017
    \draw [fill=white] (4.5,0) rectangle (5,3.9968181739); % 2760
    \draw [fill=white] (6.25,0) rectangle (6.75,4.1649057286); % 4243
    \draw [fill=white] (8,0) rectangle (8.5,3.5266990775); % 829
    \draw [fill=white] (9.75,0) rectangle (10.25,3.0372735114); % 237
    \draw [fill=white] (11.5,0) rectangle (12,2.5927322331); % 76
    \draw [fill=white] (13.25,0) rectangle (13.75,0.9); % 1

    \node [below] at (1,0) {\footnotesize $[10^2, 10^3[$};
    \node [below] at (2.75,0) {\footnotesize $[10^3, 10^4[$};
    \node [below] at (4.5,0) {\footnotesize $[10^4, 10^5[$};
    \node [below] at (6.25,0) {\footnotesize $[10^5, 10^6[$};
    \node [below] at (8,0) {\footnotesize $[10^6, 10^7[$};
    \node [below] at (9.75,0) {\footnotesize $[10^7, 10^8[$};
    \node [below] at (11.5,0) {\footnotesize $[10^8, 10^9[$};
    \node [below] at (13.25,0) {\footnotesize $[10^9, 10^{10}[$};

    \node [] at (7,-1) {\small File size in bytes};
  \end{tikzpicture}}
  \caption{Distribution of SMT-LIB benchmarks by file size (2018), for
    non-incremental~($\blacksquare$) and incremental~($\square$)
    benchmarks.}
  \label{fig:benchmark-sizes}
\end{figure}

@@

There are slightly fewer divisions than logics in the SMT Library
(Table~\ref{table:smtlib}) because not every logic contains benchmarks
eligible for the competition.  Some benchmarks typically have to be
excluded for syntactic reasons: in 2015 and 2016, 11,966 benchmarks
were excluded because they contained partial or underspecified
operations (e.g., bit-vector division) whose precise semantics were
being debated at the time.  Additionally in~2016, one benchmark was
excluded because it contained incorrect status information.  In~2017,
1,104 benchmarks were excluded because their logic had been classified
incorrectly, and 8 benchmarks were excluded because of incorrect or
missing status information.  Moreover, divisions containing datatypes
({DT})---which were new in~2017---were excluded from the unsat-core
track because of lacking tool support.  In~2018, 3,603 benchmarks were
excluded because they contained named terms (a feature of the SMT-LIB
language that is not permitted in competition benchmarks), and 5
benchmarks were excluded because of missing status information.

>>>>

The 2018 release of the SMT Library contained 336,844 non-incremental
benchmarks in 51 logics, as well as~10,167 incremental benchmarks
(with a total of nearly 32 million {\tt check-sat} commands) in 26
logics.  Table~\ref{table:smtlib} presents further data on the size of
the SMT Library since~2015.  While the library usually grows from one
year to the next because of the inclusion of new benchmarks and
logics, continuous curation efforts may also cause benchmarks to be
removed or reclassified on occasion, thereby causing individual logics
or even the entire library to shrink.  From~2015 to~2018, the total
number of benchmarks has increased by~68\,\%.  The largest benchmark
in the 2018 release had a size of 1,041~MB; the total size of the
release was 91~GB.

@@

@@

There are slightly fewer divisions than logics in the SMT Library
(Table~\ref{table:smtlib}) because not every logic contains benchmarks
eligible for the competition.  Some benchmarks typically have to be
excluded for syntactic reasons: in 2015 and 2016, 11,966 benchmarks
were excluded because they contained partial or underspecified
operations (e.g., bit-vector division) whose precise semantics were
being debated at the time.  Additionally in~2016, one benchmark was
excluded because it contained incorrect status information.  In~2017,
1,104 benchmarks were excluded because their logic had been classified
incorrectly, and 8~benchmarks were excluded because of incorrect or
missing status information.  Moreover, divisions containing datatypes
({DT})---which were new in~2017---were excluded from the Unsat-Core
track because of lacking tool support.  In~2018, 3,603~benchmarks were
excluded because they contained named terms (a feature of the SMT-LIB
language that is not permitted in competition benchmarks), and
5~benchmarks were excluded because of missing status information.
